Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-19 Methods.tex
Acronym twiddling

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic \acp{ABMs}, although see \citet{Thiele2014} for a review of alternative techniques.

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(X_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(X_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}
